Time slice analyses

### 2017-11-06 analyses/02-time-slice-analyses.Rmd
Add comments on issues

@@

>>>>

<!-- Both the above throw this error:

Error in if (is.na(data$subsamples[subsamples_check[subsample]][[1]]$elements[1, : argument is of length zero -->

@@

```
<!-- Also throws Error in if (is.na(data$subsamples[subsamples_check[subsample]][[1]]$elements[1, : argument is of length zero -->

<!-- Need to think more about the outputs here, currently they don't make much sense as there are no column headers -->
